\documentclass[]{article}
\usepackage[pdftex]{graphicx}
\usepackage[top=1in, bottom=1in, right=1.25in, left=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\begin{document}
	Meeting Minutes for Post Panel 4 (2/21/2013 and 2/25/2013)
	
	\section*{Members Present Meeting 1}
		Doublas Gabauer, Griffin Dunn, Colin Madigan, Phil Stahlfeld
	\section*{3:00 to 3:15 Panel 4 Review}
		\noindent Reviewed Material Covered in Panel 4
		\begin{itemize}
				\item Showed progress with processing automation
				\item Discussed user interface and how clients will simply drag pictures into a folder to start the processing.
				\item Discussed progress with image filtering and key frame capturing
				\item Discussed future of image processing and key frame calculation
		\end{itemize}
	
	\section*{3:15 to 3:20 Feedback}
		\begin{itemize}
			\item Asked for feedback and suggestions for current work.
				\subitem{Dr. Gabauer was pleased with our progress and told us to keep up the good work}
		\end{itemize}
	\section*{3:20 to 3:30 Future Progress}
	
			\begin{itemize}
				\item Discussed future objectives
					\subitem Dr Gabauer suggested that it would be nice to have two whiteboards captured with the camera.
					\subitem Discussed possibility of zooming out and cropping out background before image processing
					\subitem Discussed possibly defining board region using the touchscreen on camera.
				\item Discussed keystone imaging
					\subitem (Correcting for camera angle if not directly in front of board)
				
				\item Summarized what we need to do before next panel
			\end{itemize}
			
	\section*{Members Present Meeting 2}
		Robert Midkiff, Griffin Dunn, Phil Stahlfeld
	\section*{1:00 to 1:15 Panel 4 Review}
		\noindent Reviewed Material Covered in Panel 4
		\begin{itemize}
				\item Showed progress with processing automation
				\item Discussed user interface and how clients will simply drag pictures into a folder to start the processing.
				\item Discussed progress with image filtering and key frame capturing
				\item Discussed future of image processing and key frame calculation
		\end{itemize}
	\section*{1:15 to 1:25 Feedback}
		\begin{itemize}
			\item Asked for feedback and suggestions for current work.
				\subitem Dr Midkiff was very impressed by our image processing so far
				\subitem He also congratulated us on the ease of use factor (he liked that all he had to do was drag and drop)	
		\end{itemize}
	\section*{1:25 to 1:30 Future Progress}
		\begin{itemize}
			\item Asked for suggestions on future work
				\subitem Midkiff suggested that some professors would find moving through pictures in a folder too difficult and might appreciate a user interface where they could scroll through the images all at once.
		\end{itemize}	
\end{document}