\documentclass[]{article}
\usepackage[pdftex]{graphicx}
\usepackage[top=1in, bottom=1in, right=1.25in, left=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\begin{document}
	Meeting Minutes Panel 2 10/25/2012
	
	\section*{Members Present}
		Professor Watkins, Professor Thompson,, CTDI team, Griffin Dunn, Colin Madigan, Phil Stahlfeld
	\section*{15:00 to 15:05 Review}
		
		Reviewed Documentation and Technical Specifications \\
		
	\section*{15:05 to 15:15 Discussed Completed Work}
		
		\subsection*{Image Processing}
			\begin{itemize}
				\item Showed progress with Python filters
				\item Discussed ideal image quality
					\subitem{Used CamScanner as ideal to strive for}
				\item Showed progress with ImageJ filters
				\item Discussed attempts to ob
			\end{itemize}
		
		\subsection*{Sourcecode}
			\begin{itemize}
				\item Showed that ImageJ could be useful because it is open source. \\
				\item Discussed attempts at obtaining CamScanner source code. Concluded that it would be too difficult to find useable code through java decompiling. \\
				\item Prof. Thompson suggested that if Microsoft does not respond to our email soon we should talk to both him and Prof. Watkins so that they can try their contacts within Microsoft. \\
			\end{itemize}
		
	\section*{15:15 to 15:25 Discussed Future Plans}
		
		\subsection*{Discussed Gantt Chart}
			\begin{itemize}
				\item Prof Thompson suggested that we allocate more time for tasks that could be more difficult.
				\item ProPANE was asked if they had looked into OpenCV along side Python and Java filters. 
					\subitem{No, but it is scheduled into our workflow}
				\item Discussed how we planned to come up with a final plan
					\subitem{By trying many approaches and choosing those that show that they can effectively meet our goals}
			\end{itemize}
		
	
	\section*{15:25 to 15:30 Wrap Up Questions}
		
		ProPANE showed that they could 'speak in full sentences' and that they were on the right track.
	

\end{document}