\documentclass[]{article}
\usepackage[pdftex]{graphicx}
\usepackage[top=1in, bottom=1in, right=1.25in, left=1.25in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\begin{document}
	Meeting Minutes for Post Panel 5 (3/27/2013 and 3/28/2013)
	
	\section*{Members Present Meeting 1}
		Doublas Gabauer, Griffin Dunn, Colin Madigan, Phil Stahlfeld
	\section*{3:00 to 3:15 Panel 5 Review}
		\noindent Reviewed Material Covered in Panel 5
		\begin{itemize}
				\item Showed progress with process automation
				\item Discussed user interface and how clients will use second phone app to upload pictures.
				\item Discussed success with key image capturing
				\item Discussed future of image processing and image cleaning.
					\subitem Client was pleased with our image cleaning progress, but wondered about colored markers
		\end{itemize}
	
	\section*{3:15 to 3:20 Feedback}
		\begin{itemize}
			\item Asked for feedback and suggestions for current work.
				\subitem Dr. Gabauer was pleased with our progress and told us to keep up the good work
		\end{itemize}
				
	\section*{Members Present Meeting 2}
		Robert Midkiff, Griffin Dunn, Colin Madigan, Phil Stahlfeld
	\section*{8:00 to 8:15 Panel 5 Review}
		\noindent Reviewed Material Covered in Panel 5
		\begin{itemize}
				\item Showed progress with process automation
				\item Discussed user interface and how clients will use second phone app to upload pictures.
				\item Discussed success with key image capturing
				\item Discussed future of image processing and key frame calculation
		\end{itemize}
	\section*{8:15 to 8:25 Feedback}
		\begin{itemize}
			\item Asked for feedback and suggestions for current work.
				\subitem Dr Midkiff was very impressed by our image processing/cleaning so far
				\subitem He also congratulated us on the ease of use factor and liked the image cleaning progress we were able to demonstrate.
				\subitem Client suggested that he might consider actually using product in classrooms to augment current systems if we clean it up enough.
				\subitem Discussed the possibility of patenting our original work.
		\end{itemize}
\end{document}